Gaia's constraints on the very massive (initially $\sim$$150\,M_\odot$) runaway star candidate VFTS682

### 2018-06-25 VFTS682_APJL.tex
needs merger

\cite{townsley:06} did not find
an X-ray point source at the position of VFTS682 in their
\emph{Chandra} survey of the region, which suggests the absence of
colliding winds that would be expected in the presence of companions
even for extreme mass ratios, given the extremely large mass of VFTS682.
This star is also relatively isolated in \emph{Spitzer} images, except for the extended
source S10 interpreted as star formation triggered by the wind of
VFTS682 itself by \cite{walborn:13}.

@@

@@

This work has made use of data from the European Space Agency (ESA) mission {\it Gaia} (\url{https://www.cosmos.esa.int/gaia}), processed by the {\it Gaia} Data Processing and Analysis Consortium (DPAC, \url{https://www.cosmos.esa.int/web/gaia/dpac/consortium}). Funding for the DPAC has been provided by national institutions, in particular the institutions
participating in the {\it Gaia} Multilateral Agreement.

 % The background image of \Figref{fig:main} is based on observations
   % made with ESO Telescopes at the La Silla Observatory under programme
   % ID 076.C-0888, processed and released by the ESO VOS/ADP group.
   % This research made use of APLpy, an open-source plotting package for Python \citep[][]{robitaille:12}.
 \end{acknowledgements}

>>>>

The WNh5 star VFTS682, located at right ascension (RA)
05$^\mathrm{h}$38$^\mathrm{m}$55.510$^\mathrm{s}$  and declination
(DEC) \mbox{-69$^\mathrm{o}$04'26.72''} J2000, was observed as part of the multi-epoch, spectroscopic VFTS campaign covering $\lambda$4000--7000 \citep[][]{evans:11}.

\cite{townsley:06} and \textcolor{blue}{Townsley et al., in prep.} did not find
an X-ray point source at the position of VFTS682 in their
\emph{Chandra} survey of the region, which suggests the absence of
colliding winds that would be expected in the presence of companions
even for extreme mass ratios, given the extremely large mass of VFTS682.
This star is also relatively isolated in \emph{Spitzer} images, except for the extended
source S10 interpreted as star formation triggered by the wind of
VFTS682 itself by \cite{walborn:13}.

\citet{bestenlehner:11}  analyzed the spectra to infer the stellar
parameters and measure an extinction of $A_V=4.45\pm0.12$, implying a
luminosity of $\log_{10}(L/L_\odot) =  6.5\pm0.2$, making this one of
the brightest stars in the region. 
%
The star does not show clear radial velocity variations, which makes the presence of a close companion unlikely
 \citet{bestenlehner:11}. 
% 
%\emph{Chandra} survey of the region, which suggests the absence of colliding winds that would be expected in the presence of companions even for extreme mass ratios, given the extremely large mass of VFTS682.  - Selma: that depends on the separation.  I don't know what the predictions are for very unequaly winds and the LMC is far away.  I shortened it a bit and moved this up to merge it where we were discussing the presence of a companion already, to use it in the flow of the argument, instead of disrupting the flow. 
%
 Bayesian fits of the stellar parameters derived from the spectra against single star evolutionary tracks \citep{brott:11, kohler:15}
using the Bonsaii code \citep{schneider:17, schneider:18} provide
estimates for the age, present mass and initial mass, indicating that
this star among the most massive stars known, see
\Tabref{tab:star_param} for an overview of the parameters.

% Observations with the Chandra X-Ray Observatory do not reveal an X-ray point source at the position of VFTS682 \cite{townsley:06}. Such a detection would be expected if the star hosted an accreting compact object or if the strong winds of VFTS682 are colliding with those of a stellar companion. This star is also relatively isolated in \emph{Spitzer} images \citep{meixner:06}, except for the extended source S10 interpreted as star formation triggered by the wind of VFTS682 itself by \cite{walborn:13}. 
% >>>>>>> df97f49fb6e094f5c7a3bd15402c437202858eaa

@@

\SdM{VFTS682 also appears to be relatively isolated in (near) infrared.   There nearest bright (near) infrared sources detected by \emph{Spitzer}  \citep{meixner:06} and resolved in the \emph{VISTA} Magellanic Clouds Survey \citep{cioni:11} are located at a distance of about 10 arcsecond, i.e. about 2.4 pc. \cite{walborn:13} speculate that these nearby young stars may represent a case of starformation triggered by the the wind of VFTS682, but we chance alignment cannot be excluded.  }

% interpreted as star formation triggered by the wind of  VFTS682 itself by \cite{walborn:13}.   - SdM: too strong lets be more careful.  This is a controversial topic.  Walborn formulates more careful than you summarize him.

@@

This work has made use of data from the European Space Agency (ESA) mission {\it Gaia} (\url{https://www.cosmos.esa.int/gaia}), processed by the {\it Gaia} Data Processing and Analysis Consortium (DPAC, \url{https://www.cosmos.esa.int/web/gaia/dpac/consortium}). Funding for the DPAC has been provided by national institutions, in particular the institutions
participating in the {\it Gaia} Multilateral Agreement. 
\end{acknowledgements}
